MapReduce to My Ears\\ {\Large Using Big Data for Music Synthesis}

### 2013-05-10 writeup/paper.tex
Adding conclusion

>>>>

At the onset of this project, we had a vision for translating images in music and we have succeeded in doing so.
Just about every design decision in our process has room for improvement, we are pleased to have at least found a path from start to finish, though not without trials.
At every stage of the pipeline, there were new complexities to discover - the various color models and their relationships, the difficulty in using natural language to discuss color, or the vast number of parameters needed for machines to represent a piece of audio or visual art. 
However challenging though, the journey has put into perspective the amazing ability of the painter and composer to produce works of art with far more complexity than machines can manage. 
We hope that our work inspires technologists to apply their skills to reinterpret works of others from unrelated fields, and vice versa.
